rang: Reconstructing reproducible R computational environments

### 2023-06-03 paper/paper.qmd
Fix flattening

The R package `maxent` introduces a machine learning algorithm with a small memory footprint and was available on CRAN until 2019. A software paper was published by the original authors in 2012 [@jurka:2012]. The R package was also used in some subsequent automated content analytic papers [e.g. @loercher:2017:D]. Despite the editing of the package by a staffer of CRAN [^evidence], the package was removed from CRAN in 2019. (Here, we said the package `maxent` was "removed from CRAN" as per what the webpage ([https://cran.r-project.org/web/packages/maxent/index.html](https://cran.r-project.org/web/packages/maxent/index.html)) is written. However, the terminology as stated in the [CRAN Policies](https://cran.r-project.org/web/packages/policies.html#Source-packages) is "archived", quote: "Packages will not normally be removed from CRAN: however, they may be archived, including at the maintainer’s request." As all CRAN packages have all the submitted versions archived, we find this terminology confusing. Therefore, we use "removed" packages throughout this paper to indicate packages that cannot be installed by the usual method, i.e. `install.packages` but still have the old versions archived on CRAN.) We attempted to install the second last (the original submitted version) and last (with editing) versions of `maxent` on R 4.2.2. Neither worked.

@@

[^evidence]: [https://github.com/cran/maxent/commit/9d46c6aad27a1f41a78907b170ddd9a586192be9](https://github.com/cran/maxent/commit/9d46c6aad27a1f41a78907b170ddd9a586192be9)

@@

`rang` has native support for Bioconductor packages since version 0.2. We obtained the R script `"PaperFigure.R"` from the Github repository of `Sushi` [^sushi], which generates the figure in the original paper [@phanstiel:2014:S]. Similar to the above case of `ptproc`, we made a completely automated BASH script to run `"PaperFigure.R"` and get the generated figure out of the container (`Fig~\ref{fig2}`{=latex}). We made no modification to `"PaperFigure.R"`.

@@

[^sushi]: [https://github.com/PhanstielLab/Sushi/blob/master/vignettes/PaperFigure.R](https://github.com/PhanstielLab/Sushi/blob/master/vignettes/PaperFigure.R)

>>>>

The R package `maxent` introduces a machine learning algorithm with a small memory footprint and was available on CRAN until 2019. A software paper was published by the original authors in 2012 [@jurka:2012]. The R package was also used in some subsequent automated content analytic papers [e.g. @loercher:2017:D]. Despite the editing of the package by a staffer of CRAN <!-- [^evidence] -->, the package was removed from CRAN in 2019. (Here, we said the package `maxent` was "removed from CRAN" as per what the webpage ([https://cran.r-project.org/web/packages/maxent/index.html](https://cran.r-project.org/web/packages/maxent/index.html)) is written. However, the terminology as stated in the [CRAN Policies](https://cran.r-project.org/web/packages/policies.html#Source-packages) is "archived", quote: "Packages will not normally be removed from CRAN: however, they may be archived, including at the maintainer’s request." As all CRAN packages have all the submitted versions archived, we find this terminology confusing. Therefore, we use "removed" packages throughout this paper to indicate packages that cannot be installed by the usual method, i.e. `install.packages` but still have the old versions archived on CRAN.) We attempted to install the second last (the original submitted version) and last (with editing) versions of `maxent` on R 4.2.2. Neither worked.

@@

<!-- [^evidence]: [https://github.com/cran/maxent/commit/9d46c6aad27a1f41a78907b170ddd9a586192be9](https://github.com/cran/maxent/commit/9d46c6aad27a1f41a78907b170ddd9a586192be9) -->

@@

`rang` has native support for Bioconductor packages since version 0.2. We obtained the R script `"PaperFigure.R"` from the Github repository of `Sushi` <!-- [^sushi] -->, which generates the figure in the original paper [@phanstiel:2014:S]. Similar to the above case of `ptproc`, we made a completely automated BASH script to run `"PaperFigure.R"` and get the generated figure out of the container (`Fig~\ref{fig2}`{=latex}). We made no modification to `"PaperFigure.R"`.

@@

<!-- [^sushi]: [https://github.com/PhanstielLab/Sushi/blob/master/vignettes/PaperFigure.R](https://github.com/PhanstielLab/Sushi/blob/master/vignettes/PaperFigure.R) -->
